localHierarchy

### 2025-10-15 README.Rmd
fix stan file paths; fix article; add vignette

---
output: github_document
---

@@

# localHierarchy

The `localHierarchy` R package provides functionality for fitting Bayesian hierarchical models in settings where both global and local estimation is required. The package provides R functions and Stan model components to support global modeling, in which all parameters in hierarchical models are estimated, and local modeling, where parameters are estimated for only one or a small number of populations, using fixed values from a global model fit.

## Installation

-   Dependency on `cmdstanr:` Instructions for installing `cmdstanr` are available in their [Getting started](https://mc-stan.org/cmdstanr/articles/cmdstanr.html) guide.

@@

## Examples

to do: add from paper

>>>>

---
title: "localHierarchy"
output: github_document
---

@@

# Background

Bayesian hierarchical models are widely used in global health estimation, where data availability may vary across national or subnational populations. Such models are typically fitted to a global database, e.g., to produce national-level estimates for all countries in the world or in some region. To facilitate analysis at a local level, models are often desirable that are informed by global models but can be fitted to just a subset of the data, such as data for one country. We refer to such models as local models: models that are derived from global hierarchical models but adapted such that they can be fitted to the data from one population alone.

The `localHierarchy` R package provides functionality for fitting Bayesian hierarchical models in settings where both global and local estimation is required. The package provides R functions and Stan model components to support global modeling, in which all parameters in hierarchical models are estimated, and local modeling, in which parameters are estimated for only one or a small number of populations, using fixed values from a global model fit.

The article on this website presents a practical introduction to the package for the applied user and illustrates the package’s functionality through examples for national and subnational estimation.

# Installation

-   `localHierarchy` depends on `cmdstanr:` Instructions for installing `cmdstanr` are available in their [Getting started](https://mc-stan.org/cmdstanr/articles/cmdstanr.html) guide.

@@

# Examples

See vignette and article.
